Paper notes

### 2019-08-12 paper_notes.Rmd
Add files via upload

\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- <- this is a command to appear in pdf -->
<!-- command not to appear in pdf -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.lp="fig:")

library(Hmisc)
library(ggplot2)
library(gridExtra)
library(ggpubr)
# Here functions that are used.

# Calculation ethnic utility (for each option)
# i_e: ethnic threshold (ideal point)
# M: right-side slope
# x: number agents in neighborhood with same color
# n: total number agents in neighborhood
# S: left-side slope
# Note: if (x > n){U <- NA} to show the case number of agents in neighborhood different from 8, so that utility is calculated based on this, although x-axis in graph has 8 points  (excluded from calculation)

@@

@@

# symmetric
# constant
# threshold

@@

e_w <- 0.8
v_w <- 1 - e_w

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.lp="fig:")

library(Hmisc)
library(ggplot2)
library(gridExtra)
library(ggpubr)

# Here functions that are used.

# Calculation ethnic utility (for each option)
# i_e: ethnic threshold (ideal point)
# M: right-side decreasing slope
# x: number agents in neighborhood with same color
# n: total number agents in neighborhood
# S: left-side increasing slope
# Note: if (x > n){U <- NA} to show the case number of agents in neighborhood different from 8, so that utility is calculated based on this, although x-axis in graph has 8 points  (excluded from calculation)

@@

The basic idea is to introduce a beta distribution for $\beta$ in the utility definition of neighborhood $j$ for agent $i$ :

$$
U_{(xj,yj)}   = \beta_xx_j + \beta_yy_j + \epsilon_j
$$

With $\beta_x$ the importance of ethnic composition $x_j$ of neighborhood $j$ and $\beta_y$ its value composition $y_i$.

To avoid confusion between parameter beta and beta distribution used in the simulation, $\beta_x$ is called ethnic weight (ew in R code), $\beta_y$ is called value weight (v_w in R code).

We want to compare different type of functions, in particular to compare the single-peaked function as modeled by [@zhang2011, graphic p. 174] with the Schelling's original threshold we also  used in the ACS paper, and a mixed one where utility increases until the ideal point as in Zhang, and remains constant at max. 1 when the ethnic composition exceeds the ideal point. The last function comes from the idea that it can be a realistic scenario in people's relocation choice.

To have all of the functions coming from the same computation and reduce as much, I modified @zhang2011's formula, assuming max Utility = 1 and introducing 2 parameters to the formula, as in the simulation:\par
* $S[0,1]$, regulating the increasing left slope
* $M[0,1]$, regulating the decreasing right slope (as in Zhang)

$$
U=
\begin{cases}
1, & \text{if} \ \frac{x}{n} = np, \\
\frac{x}{np}\times S, & \text{if} \ x < np, \\
M + ((1 - \frac{x}{n}) \times (1 - M)) / (1 - p), & \text{if} \ x > np
\end{cases}
$$

@@

symmetric
 constant
 threshold

@@

e_w <- 1
v_w <- 1-e_w
